Information Closure Theory of Consciousness

### 2020-04-08 ICT_Frontiers_rev202001.tex
Changed Figure 2

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv_2.pdf}
					\caption{The dependencies between a system and its environment.} % Figure adapted from \cite{BERTSCHINGER.2006}
					\label{fig:SystemAndEnv}
				\end{figure}

>>>>

				\begin{figure}
					\includegraphics[width=\textwidth]{Submission/Frontiers/SystemAndEnv_3.pdf}
					\caption{The dependencies between a system  $Y$ and its environment $E$ through the channels $\hat{y_t}$ and $\hat{e_t}$.} % Figure adapted from \cite{BERTSCHINGER.2006}
					\label{fig:SystemAndEnv}
				\end{figure}
